\documentclass[10pt,colorlinks=true,urlcolor=blue]{moderncv}
\usepackage{utopia}
\moderncvtheme[blue]{classic}
\usepackage[utf8]{inputenc}
\usepackage{multibbl}
\newbibliography{pub}
\newbibliography{techreports}
\newbibliography{talks}
\newbibliography{misc}
\newbibliography{conf}
\pagenumbering{arabic}
\usepackage{lastpage}
\rfoot{\addressfont\itshape\textcolor{gray}{Page \thepage\ of \pageref{LastPage}}}
%\newbibliography{talks}
\usepackage[scale=0.8]{geometry}
\newcommand{\cvdoublecolumn}[2]{%
  \cvline{}{}{%
    \begin{minipage}[t]{\listdoubleitemmaincolumnwidth}#1\end{minipage}%
    \hfill%
    \begin{minipage}[t]{\listdoubleitemmaincolumnwidth}#2\end{minipage}%
    }%
}

% usage: \cvreference{name}{address line 1}{address line 2}{address line 3}{address line 4}{e-mail address}{phone number}
% Everything but the name is optional
% If \addresssymbol, \emailsymbol or \phonesymbol are specified, they will be used.
% (Per default, \addresssymbol isn't specified, the other two are specified.)
% If you don't like the symbols, remove them from the following code, including the tilde ~ (space).

\newcommand{\cvreference}[7]{%
    \textbf{#1}\newline% Name
    \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
    \ifthenelse{\equal{#3}{}}{}{#3\newline}%
    \ifthenelse{\equal{#4}{}}{}{#4\newline}%
    \ifthenelse{\equal{#5}{}}{}{#5\newline}%
    \ifthenelse{\equal{#6}{}}{}{\emailsymbol~\texttt{#6}\newline}%
    \ifthenelse{\equal{#7}{}}{}{\phonesymbol~#7}}

  \AtBeginDocument{\recomputelengths} \firstname{Minh}
  \familyname{Tang} \address{Applied Mathematics and Statistics \\
    Johns Hopkins University \\ 3400 N. Charles St}{Baltimore, MD
    21218} \email{mtang10@jhu.edu}
  \homepage{www.cis.jhu.edu/\textasciitilde minh}
\begin{document}
\maketitle
\section{Education}
\cventry{2010}{Ph.D in Computer Science}{\newline Indiana University Bloomington}{}{}{}
\cventry{2004}{M.S. in Computer Science}{\newline University of Wisconsin Milwaukee}{}{}{}
\cventry{2001}{B.S. in Computer Science}{\newline Assumption University, Thailand}{}{}{}

\section{Work Experience}
\cventry{01/17 -- now}{Associate Research Professor}
{\newline Department of Applied Mathematics and Statistics, Johns Hopkins University}{}{}{}

\cventry{07/14 -- 12/16}{Assistant Research Professor}
{\newline Department of Applied Mathematics and Statistics, Johns Hopkins University}{}{}{}
\cventry{10/10 -- 06/14}{Postdoctoral Fellow}{\newline Department of
  Applied Mathematics and Statistics, Johns Hopkins
  University}{}{}{}

\section{Research Interests}
\cvline{}{statistical pattern recognition, dimensionality reduction,
  statistical inference on graphs}{}

\section{Grants and Research Award}

\cvline{\small 03/17 -- 08/21}{co-PI on DARPA Data-Driven Discovery of Models (PI: Carey Priebe)}

\cvline{\small 08/18 -- 08/19}{PI on Microsoft Research Award: Efficiency and Optimality in Graph Inference}

\section{Journal Publications}

\cvline{2018+}{J.~Cape and \textbf{M.~Tang} and C.~E.~Priebe. Signal-plus-noise matrix models: eigenvector deviations and fluctuations. {\em Biometrika}, accepted for publication. arXiv preprint at \url{http://arxiv.org/abs/1802.00381}}

\cvline{2018+}{A.~Athreya and \textbf{M.~Tang} and Y.~Park and C.~E.~Priebe. On estimation and inference in latent structure random graphs. {\em Statistical Science}, accepted for publication. arXiv preprint at \url{http://arxiv.org/abs/1806.01401}}

\cvline{2018+}{J.~Cape and \textbf{M.~Tang} and C.~E.~Priebe. The
two-to-infinity norm and singular subspace geometry with applications
to high-dimensional statistics. {\em Annals of Statistics}, accepted for publication. arXiv
preprint at \url{http://arxiv.org/abs/1705.08917}.}

\cvline{2018}{\textbf{M.~Tang} and C.~E.~Priebe. Limit theorems for
eigenvectors of the normalized Laplacian for random graphs. {\em
Annals of Statistics}, Vol. 46, pp. 2360--2415}

\cvline{2018}{A.~Athreya and D.~E.~Fishkind and K.~Levin and
V.~Lyzinski and Y.~Park and Y.~Qin and D.~L.~Sussman and
\textbf{M.~Tang} and J.~T.~Vogelstein and C.~E.~Priebe, Statistical
inference on random dot product graphs: a survey, {\em Journal of
Machine Learning Research}, Vol. 18.}

\cvline{2017}{J.~Cape, \textbf{M.~Tang} and C.~E.~Priebe. The
Kato-Temple inequality and eigenvalue concentration. {\em Electronic
Journal of Statistics}, Vol. 11, pp. 3954--3978.}

\cvline{2017}{V.~Lyzinski, \textbf{M.~Tang}, A.~Athreya, Y.~Park and
C.~E.~Priebe. Community detection and classification in hierarchical
stochastic blockmodels. {\em IEEE Transactions on Network Science and
Engineering}, Vol.  4, pp. 13--26.}

\cvline{2017}{\textbf{M.~Tang}, A.~Athreya, D.~L.~Sussman,
V.~Lyzinski, Y.~Park and C.~E.~Priebe. A semiparametric two-sample
hypothesis testing problem for random graphs. {\em Journal of
Computational and Graphical Statistics}, Vol.  26, pp. 344--354.}

\cvline{2017}{\textbf{M.~Tang}, A.~Athreya, D.~L.~Sussman,
V.~Lyzinski, and C.~E.~Priebe. A nonparametric two-sample hypothesis
testing problem for random dot product graphs. {\em Bernoulli},
Vol. 23, pp. 1599--1630.}

\cvline{2016}{S.~Suwan, D.~S.~Lee, R.~Tang, D.~L.~Sussman,
\textbf{M.~Tang} and C.~E.~Priebe. Empirical Bayes estimation for the
stochastic blockmodel. {\em Electronic Journal of Statistics},
Vol. 10, pp. 761--782.}

\cvline{2016}{ A.~Athreya, V.~Lyzinski, D.~J.~Marchette, C.~E.~Priebe,
D.~L.~Sussman and \textbf{M.~Tang}.  A central limit theorem for
scaled eigenvectors of random dot product graphs. {\em Sankhya Series
A}, Vol. 78, pp. 1--18.}

\cvline{2015}{ C.~E.~Priebe, D.~L.~Sussman, \textbf{M.~Tang} and
J.~T.~Vogelstein. Statistical inference on errorfully observed
graphs. {\em Journal of Computational and Graphical Statistics},
Vol. 24, pp. 930--953.}

\cvline{2014}{ V.~Lyzinski, D.~L.~Sussman, \textbf{M.~Tang},
A.~Athreya and C.~E.~Priebe. Perfect clustering for stochastic
blockmodel graphs via adjacency spectral embedding. {\em Electronic
Journal of Statistics}, Vol 8, pp. 2905--2922.}

\cvline{2014}{ C.~Shen, M.~Sun, \textbf{M.~Tang} and
C.~E.~Priebe. Generalized canonical correlation analysis for
classification in high dimensions. {\em Journal of Multivariate
Analysis}, Vol. 130, pp. 310--322.}

\cvline{2014}{D.~L.~Sussman, \textbf{M.~Tang} and
C.~E.~Priebe. Consistent latent position estimation and vertex
classification for random dot product graphs. {\em IEEE Transactions
on Pattern Analysis and Machine Intelligence}, Vol. 36, pp. 48--57.}

\cvline{2014}{H.~Wang, \textbf{M.~Tang}, Y.~Park, and
C.~E.~Priebe. Locality statistics for anomaly detection in time-series
of graphs. {\em IEEE Transactions on Signal Processing.}, Vol. 62,
pp. 703--717.}

\cvline{2013}{D.~E.~Fishkind, D.~L.~Sussman, \textbf{M.~Tang},
J.~T.~Vogelstein, and C.~E.~Priebe. Consistent adjacency-spectral
partitioning for the stochastic block model when the model parameters
are unknown. {\em SIAM Journal on Matrix Analysis and Applications},
Vol. 34, pp. 23--39.}

\cvline{2013}{N.~H.~Lee, J.~Yoder, \textbf{M.~Tang} and C.~E.~Priebe.
On latent position inference from doubly stochastic messaging
activities. {\em Multiscale Modeling and Simulation}, Vol. 11,
pp. 683--718.}

\cvline{2013}{M.~Sun, C.~E.~Priebe and \textbf{M.~Tang}. Generalized
canonical correlation analysis for disparate data fusion. {\em Pattern
Recognition Letters}, Vol. 34, pp. 194--200.}

\cvline{2013}{\textbf{M.~Tang}, Y.~Park, N.~H.~Lee and C.~E.~Priebe.
Attribute fusion in a latent process model for time series of
graphs. {\em IEEE Transactions on Signal Processing}, Vol. 61,
pp. 1721--1732.}

\cvline{2013}{\textbf{M.~Tang} and D.~L.~Sussman and
C.~E.~Priebe. Universally consistent vertex classification for latent
positions graphs. {\em Annals of Statistics}, Vol. 41,
pp. 1406--1430.}

\cvline{2012}{D.~L.~Sussman, \textbf{M.~Tang}, D.~E.~Fishkind and
C.~E.~Priebe. A consistent adjacency spectral embedding for stochastic
blockmodel graphs. {\em Journal of the American Statistical
Association}, Vol. 107, pp. 1119--1128.}

\section{Preprints}
\cvline{2018}{C.~E.~Priebe and Y.~Park and J.~T.~Vogelstein and J.~M.~Conroy and V.~Lyzinski and \textbf{M.~Tang} and A.~Athreya and J.~Cape and E.~Bridgeford. On a 'two truths' phenomenon in spectral graph clustering. arXiv preprint at \url{http://arxiv.org/abs/1808.07801}}
\cvline{2018}{G.~Li and \textbf{M.~Tang} and N.~Charon and C.~E.~Priebe. A central limit theorem for classical multidimensional scaling. arXiv preprint at \url{http://arxiv.org/abs/1804.00631}.}
\cvline{2018}{\textbf{M.~Tang}. The eigenvalues of stochastic blockmodel graphs.arXiv preprint at \url{http://arxiv.org/abs/1803.11551}.}
\cvline{2018}{P.~Rubin-Delanchy and C.~E.~Priebe and \textbf{M.~Tang} and J.~Cape. A statistical interpretation of spectral embedding: the generalised random dot product graph.
arXiv preprint at \url{http://arxiv.org/abs/1709.05506}.}
\cvline{2017}{\textbf{M.~Tang} and J.~Cape and
C.~E.~Priebe. Asymptotically efficient estimators for stochastic
blockmodels: the naive MLE, the rank-constrained MLE, and the
spectral. arXiv preprint at
\url{http://arxiv.org/abs/1710.10936}.}
\cvline{2017}{J.~T.~Vogelstein and \textbf{M.~Tang} and E.~Bridgeford
and D.~Zheng and R.~Burns and M.~Maggioni. Linear optimal low rank
projection for high-dimensional multi-class data. arXiv preprint at \url{http://arxiv.org/abs/1709.01233}}
\cvline{2017}{R.~Tang and \textbf{M.~Tang} and J.~T.~Vogelstein and
C.~E.~Priebe. Robust estimation from multiple graphs under gross error
contamination. arXiv preprint at
\url{http://arxiv.org/abs/1707.03487}.}
\cvline{2017}{K.~Levin and A.~Athreya and \textbf{M.~Tang} and
C.~E.~Priebe and V.~Lyzinski. A central limit theorem for an omnibus
embedding of random dot product graphs. arXiv preprint at \url{http://arxiv.org/abs/1705.08832}.}
\cvline{2017}{P.~Rubin-Delanchy and C.~E.~Priebe and \textbf{M.~Tang}.
Consistency of adjacency spectral embedding for the mixed membership
stochastic blockmodel. arXiv preprint at
\url{http://arxiv.org/abs/1705.04518}.}
\cvline{2017}{C.~E.~Priebe and Y.~Park and \textbf{M.~Tang} and
A.~Athreya and V.~Lyzinski and J.~T.~Vogelstein and Y.~Qin and
B.~Cocanougher and K.~Eichler and M.~Zlatic and
A.~Cardona. arXiv preprint at \url{http://arxiv.org/abs/1704.03297}.}
\cvline{2016}{A.~Athreya, \textbf{M.~Tang}, V. Lyzinski, Y.Park,
B.~Lewis, M.~Kane, and C.~E.~Priebe.  Numerical tolerance for spectral
decompositions of random dot product graphs. arXiv preprint at
\url{http://arxiv.org/abs/1608.00451}.}
\cvline{2013}{\textbf{M.~Tang}, Y.~Park and
C.~E.~Priebe. Out-of-sample extension for latent position
graphs. arXiv preprint at \url{http://arxiv.org/abs/1305.4893}.}

% \nocite{pub}{*}
% \nocite{conf}{*}
% \nocite{misc}{*}
% \nocite{talks}{*}
% \bibliographystyle{pub}{cv}
% \bibliography{pub}{cv1}{Journal articles}
% \bibliographystyle{misc}{cv}
% \bibliography{misc}{cv2}{Preprints}

\

 \section{Invited Talks}
\cvline{\small 09/2017}{Department of Mathematics and Statistics, Boston University.}
\cvline{\small 08/2017}{Joint Statistical Meetings, Baltimore, MD, USA.}
\cvline{\small 11/2015}{Department of Statistics, Indiana University Bloomington.}
\cvline{\small 02/2015}{School of Industrial and Systems Engineering, 
  Georgia Institute of Technology.}
\cvline{\small 02/2015}{Department of Statistics, Virginia Tech.} 
\cvline{\small 08/2014}{Joint Statistical Meetings, Boston, MA, USA.}
\cvline{\small 05/2012}{Interface Symposia, Houston, TX, USA.}

% \bibliographystyle{conf}{cv}
% \bibliography{conf}{cv4}{Conference articles}

%\cventry{\small Pending}{co-PI}{}{JHU Science of Learning Institute}{The ABC's of fusion and inference from multiple
%  connectome modalities (PI: Youngser Park)}{}
%\cventry{\small Pending}{PI}{}{National Science Foundation}{Algorithmic and theoretical advances for community detection and classification in hierarchical networks (co-PI: Vince Lyzinski)}{}
%\cventry{\small 2012--2017}{Key Personnel}{}{Defense Advanced Research
%  Projects Agency}{DARPA XDATA: Fusion and Inference from Multiple
%  and Massive Disparate Distributed Dynamic Data Sets (PI: Carey Priebe)}{}
%\cventry{\small 2014--2016}{Key Personnel}{}{National Science
%  Foundation}{NSF Brain Eager: Discovery and characterization of
%  neural circuitry from behavior, connectivity patterns and activity
%  patterns (PI: Carey Priebe)}{}
%
\section{Teaching}

\cvline{JHU}{Generalized linear mixed models \& longitudinal data analysis (Spring 2017 \& 2018)}
\cvline{JHU}{Professor Joel Dean Award for Excellence in
Teaching (Spring 2016)}
\cvline{JHU}{Topics in statistical pattern
recognition (Spring 2016)}
\cvline{JHU}{Applied statistics and data analysis (Fall 2013 -- Fall 2017)}
\cvline{JHU}{Statistical learning and high-dimensional data
analysis (Spring 2011)}

\section{Mentoring}
\cvline{JHU}{Dissertation committee: Cencheng Shen (2015; second
reader), Heng Wang (2015), Jordan Yoder (2016), Runze Tang (2017;
second reader), Shangsi Wang (2018).}

\cvline{JHU}{Research Advising: Joshua Cape (2015 -- present)}

\section{Professional Services}
\cvline{}{Refereed papers for {\em Annals of Statistics}, {\em Annals of Applied Statistics}, {\em Statistical Science}, {\em Journal
    of Computational and Graphical Statistics}, {\em IEEE Transactions
    on Signal Processing}, {\em IEEE Transactions on Network Science},
  {\em Electronic Journal of Statistics}, {\em Journal of Machine
    Learning Research}, {\em IEEE Transactions on Knowledge and Data
    Engineering}. }

\section{References}
\cvdoublecolumn{\cvreference{Michael W. Trosset}
    {Department of Statistics}
    {Indiana University Bloomington}
    {919 E. 10th St}
    {Bloomington, IN 47408, USA.}
    {mtrosset@indiana.edu}
{}%
}
{\cvreference{Carey E. Priebe}
    {Applied Mathematics and Statistics}
    {Johns Hopkins University}
    {3400 N. Charles St}
    {Baltimore, MD 21218, USA.}
    {cep@jhu.edu}
{}%
    }

\cvdoublecolumn{\cvreference{Dirk Van Gucht}
    {School of Informatics, Computing and Engineering}
    {Indiana University Bloomington}
    {700 N. Woodlawn Ave}
    {Bloomington, IN 47405, USA.}
    {vgucht@indiana.edu}
{}%
    }
    {\cvreference{Laurent Younes}
    {Applied Mathematics and Statistics}
    {Johns Hopkins University}
    {3400 N. Charles St}
    {Baltimore, MD 21218, USA.}
    {laurent.younes@jhu.edu}
{}%
    }
    
% \cvdoublecolumn{\cvreference{Thitipong Tanprasert}
%    {Faculty of Science and Technology}
%    {Assumption University}
%    {Ramkhamhaeng Soi 24}
%    {Hua Mak, Bangkok 10240, Thailand.}
%    {thitipong@sci-tech.au.edu}
% {}%
% {}
%    }
%    {\cvreference{Donniell E. Fishkind}
%    {Applied Mathematics and Statistics}
%    {Johns Hopkins University}
%    {3400 N. Charles St}
%    {Baltimore, MD 21218, USA.}
%    {def@jhu.edu}
% {}%
%}

\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
